A bootstrap-based comparison of ILI intensity thresholds from the moving epidemic and WHO methods: Derivations

### 2021-02-10 Draft/Derivations_MEM.tex
Updating drafts.

Empirically, after transformation to the log scale, the variance of season peak values is low (between 0.02 and 0.4 for the adta sets analysed in Section \textbf{XXX} of the main manuscript). The resulting variances of $q_{Y, \alpha}$ are likewise quite small and do not play an importnat role in equation \eqref{eq:taylor}. We can thus use the even simpler approximation
\begin{equation}
\mathbb{E}(q_\alpha) \approx \exp\left\{\mathbb{E}(q_{Y, \alpha})\right\}.
\end{equation}

>>>>

Empirically, after transformation to the log scale, the variance of season peak values is low (between 0.02 and 0.4 for the data sets analysed in Section 5 of the main manuscript). The resulting variances of $q_{Y, \alpha}$ are then quite small and do not play an important role in equation \eqref{eq:taylor}. We can thus use the even simpler approximation
\begin{equation}
\mathbb{E}(q_\alpha) \approx \exp\left\{\mathbb{E}(q_{Y, \alpha})\right\}.
\end{equation}
